COG-ED Manuscript

### 2021-10-19 06_Paper/COG-ED/Manuscript.Rmd
started the new AUC calculation
Not finished

## Hypotheses
Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load measures we hypothesized that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
Regarding the associations of task load and ED we hypothesized that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
And regarding individual differences in ED we hypothesized that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
However, since NFC is conceptually related to cognitive but not physical effort, we added the hypothesis that (3c) perceived mental load and perceived effort predict individual NFC scores.

@@

## Analysis
We aimed to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom in the statistical procedures.
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Ashby1980; @Whelan2008; @Berger2021].
Post-error trials were also excluded, because RT on those trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method was used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**
The association of ED and NFC was examined using three separate regressions.
One regression used the AUC of each participant's SVs to predict their NFC score.
The second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
And the last regression used the AUC of each participant's SV, the AUC of the NASA-TLX mental load subscale, and the AUC of the NASA-TLX effort subscale to predict each participant's NFC score.

@@

  # H3c: The NASA-TLX dimensions effort and mental load predict individual NCS scores.

  # compute multiple linear regression to predict NCS based on SV AUC, Effort AUC and Mental Load AUC

  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv + h3_data$auc_mental + h3_data$auc_effort))

>>>>

## Hypotheses
Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load measures we hypothesized that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
Regarding the associations of task load and ED we hypothesized that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
And regarding individual differences in ED we hypothesized that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
However, we propose that (3c) when taking individual preferences for different n-back levels into account, the prediction of NFC scores by SVs can be improved significantly.

@@

## Analysis
We aimed to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom in the statistical procedures.
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Ashby1980; @Whelan2008; @Berger2021].
Post-error trials were also excluded, because RT on those trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method was used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**
The association of ED and NFC was examined using three separate regressions.
One regression used the AUC of each participant's SVs to predict their NFC score.
The second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
And the last regression **insert method**.

@@

  # H3c: When putting the SVs in descending order before computing the AUC, the prediction of NFC scores by SVs can be improved significantly.

  h3c_data <- data.frame(subject = character(), auc_sv = double())

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = TRUE))
    h3c_data <- rbind(h3c_data, newdata)

  # compute linear regression to predict NCS based on SV AUC

  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))
